\newacronym[%
  shortplural={PCAs},%
  longplural={Principal Component Analyses}%
] {pca}{PCA}{Principal Component Analysis}

\newacronym[] {pdf}{PDF}{Portable Document Format}

\longnewglossaryentry{scm}{%
  name={SCM}}%
{%
Supply Chain Management}

\longnewglossaryentry{anac}{%
  name={ANAC}}%
{%
The International Automated Negotiating Agents Competition (ANAC) is an annual event, held in conjunction with the International Joint Conference on Autonomous Agents and Multi-Agent Systems (AAMAS), or the International Joint Conference on Artificial Intelligence (IJCAI). The ANAC competition brings together researchers from the negotiation community and provides unique benchmarks for evaluating practical negotiation strategies in multi-issue domains. The competitions have spawned novel research in AI in the field of autonomous agent design which are available to the wider research community.
}

\longnewglossaryentry{scml}{%
  name={SCML}}%
{%
Supply Chain Management League one of ANAC 2020 and 2021 leagues @ IJCAI 2020 and 2021.}

\longnewglossaryentry{saom}{%
  name={SAOM}}%
{%
Stacked Alternating Offers Protocol, namely in SCML also as Stacked Alternating Offers Mechanism.
}

\longnewglossaryentry{mdps}{%
  name={MDPs}}%
{%
Markov decision process.
}

\longnewglossaryentry{mdp}{%
  name={MDP}}%
{%
Markov decision process.
}

\longnewglossaryentry{negmas}{%
  name={NegMAS}}%
{%
NEGotiation MultiAgent System
}

\longnewglossaryentry{pytorch}{%
  name={PyTorch}}%
{%
Python machine learning framework, developed by...
}

\longnewglossaryentry{openai gym}{%
  name={OpenAI Gym}}%
{%
OpenAI Gym is a toolkit for reinforcement learning research. It includes a growing collection of benchmark problems that expose a common interface, and a website where people can share their results and compare the performance of algorithms.
}

\longnewglossaryentry{ray}{%
  name={Ray}}%
{%
Ray provides a simple, universal API for building distributed applications.
}

\longnewglossaryentry{qmix}{%
  name={QMIX}}%
{%
Monotonic Value Function Factorisation for Deep Multi-Agent Reinforcement Learning
}

\longnewglossaryentry{dpg}{%
  name={DPG}}%
{%
Deterministic Policy Gradient
}

\longnewglossaryentry{ddpg}{%
  name={DDPG}}%
{%
Deep Deterministic Policy Gradient
}

\longnewglossaryentry{maddpg}{%
  name={MADDPG}}%
{%
Multi Agent Deep Deterministic Policy Gradient
}

\longnewglossaryentry{anegma}{%
  name={ANEGMA}}%
{%
ANEGMA
}

\longnewglossaryentry{rlboa}{%
  name={RLBOA}}%
{%
RLBOA
}

\longnewglossaryentry{negosi}{%
  name={NegoSI}}%
{%
negotiation-based MARL with sparse interactions (NegoSI)
}

\longnewglossaryentry{cns}{%
  name={CNS}}%
{%
Concurrent negotiation strategy.
}

\longnewglossaryentry{rl}{%
  name={RL.}}%
{%
Reinforcement learning.
}

\longnewglossaryentry{drl}{%
  name={DRL}}%
{%
Deep reinforcement learning.
}

\longnewglossaryentry{madrl}{%
  name={MADRL}}%
{%
Multi-Agent Deep reinforcement learning.
}

\longnewglossaryentry{marl}{%
  name={MARL}}%
{%
Multi-Agent Reinforcement Learning.
}

\longnewglossaryentry{sbe}{%
  name={SBE}}%
{%
Single-agent bilateral negotiation environment.
}

\longnewglossaryentry{mcbe}{%
  name={MCBE}}%
{%
Multi-agent concurrent bilateral negotiation environment.
}

\longnewglossaryentry{dqn}{%
  name={DQN}}%
{%
Deep Q-Value Network
}

\longnewglossaryentry{ppo}{%
  name={PPO}}%
{%
Proximal Policy Optimization
}

\longnewglossaryentry{pg}{%
  name={PG}}%
{%
Policy Gradient
}

\longnewglossaryentry{scml-oneshot}{%
  name={SCML-OneShot}}%
{%
OneShot World in SCML.
}

\longnewglossaryentry{my-one-shot-drl-agent}{%
  name={MyOneShotBasedAgent}}%
{%
My Deep Reinforcement Learning Agent in SCM-ONESHOT
}

\longnewglossaryentry{greedy-one-shot-agent}{%
  name={GreedyOneShotAgent}}%
{%
A greedy agent based on OneShotAgent
}

\longnewglossaryentry{ind-dec-agent}{%
  name={IndDecentralizingAgent}}%
{%
Independent Centralizing Agent, implemented in standard scml
}

\longnewglossaryentry{ann}{%
  name={ANN}}%
{%
Artificial Neural Network
}

\longnewglossaryentry{td}{%
  name={TD}}%
{%
Temporal Error.
}

\longnewglossaryentry{vdn}{%
  name={VDN}}%
{%
Value Decomposition Networks
}

\longnewglossaryentry{boa}{%
  name={BOA}}%
{%
the bidding strategy, the opponent model, and the acceptance strategy
}

